\paperTitle

### 2014-06-21 doc/icml2014/icml2014-presentation/diagrams.tex
Updated figures, used an outline slide, and updatd setup

\newcommand<>{\drawgen}[1]{%
  \uncover#2{
    \point{start-gen}{#1}
    \node[style=node] (h) at (start-gen) {$h$};
%    \node[left=0.1cm of h] {$h$};
    \node[style=obsnode,below=1cm of h] (x2) {$x_2$};
    \node[style=obsnode,left=0.5cm of x2] (x1) {$x_1$};
    \node[style=obsnode,right=0.5cm of x2] (x3) {$x_3$};
    \draw[-latex] (h) -- (x1);
    \draw[-latex] (h) -- (x2);
    \draw[-latex] (h) -- (x3);
  }
}

\newcommand<>{\drawgensquiggle}[1]{%
  \uncover#2{
    \point{start-gen}{#1}
    \node[style=node] (h) at (start-gen) {$h$};
%    \node[left=0.1cm of h] {$h$};
    \node[style=obsnode,below=1cm of h] (x2) {$x_2$};
    \node[style=obsnode,left=0.5cm of x2] (x1) {$x_1$};
    \node[style=obsnode,right=0.5cm of x2] (x3) {$x_3$};
    \draw[-latex,squiggle] (h) -- (x1);
    \draw[-latex,squiggle] (h) -- (x2);
    \draw[-latex,squiggle] (h) -- (x3);
  }
}

\newcommand<>{\drawdisc}[1]{%
  \uncover#2{
    \point{start-disc}{#1}
    \node[style=node] (h) at (start-disc) {};
    \node[right=0.1cm of h] {$h$};

@@

>>>>

\newcommand<>{\drawgen}[1]{%
  \uncover#2{
    \point{start-gen}{#1}
    \node[style=node] (h) at (start-gen) {$h_1$};
%    \node[left=0.1cm of h] {$h$};
    \node[style=obsnode,below=1cm of h] (x2) {$x_2$};
    \node[style=obsnode,left=0.5cm of x2] (x1) {$x_1$};
    \node[style=obsnode,right=0.5cm of x2] (x3) {$x_3$};
    \draw[-latex] (h) -- (x1);
    \draw[-latex] (h) -- (x2);
    \draw[-latex] (h) -- (x3);
  }
}

\newcommand<>{\drawgensquiggle}[1]{%
  \uncover#2{
    \point{start-gen}{#1}
    \node[style=node] (h) at (start-gen) {$h_1$};
%    \node[left=0.1cm of h] {$h$};
    \node[style=obsnode,below=1cm of h] (x2) {$x_2$};
    \node[style=obsnode,left=0.5cm of x2] (x1) {$x_1$};
    \node[style=obsnode,right=0.5cm of x2] (x3) {$x_3$};
    \draw[-latex,squiggle] (h) -- (x1);
    \draw[-latex,squiggle] (h) -- (x2);
    \draw[-latex,squiggle] (h) -- (x3);
  }
}

\newcommand<>{\drawgensquigglescale}[2]{%
  \uncover#3{
    \point{start-gen}{#1}
    \node[style=node,scale=#2] (h) at (start-gen) {$h_1$};
%    \node[left=0.1cm of h] {$h$};
    \node[style=obsnode,below=1cm of h,scale=#2] (x2) {$x_2$};
    \node[style=obsnode,left=0.5cm of x2,scale=#2] (x1) {$x_1$};
    \node[style=obsnode,right=0.5cm of x2,scale=#2] (x3) {$x_3$};
    \draw[-latex,squiggle,scale=#2] (h) -- (x1);
    \draw[-latex,squiggle,scale=#2] (h) -- (x2);
    \draw[-latex,squiggle,scale=#2] (h) -- (x3);
  }
}

\newcommand<>{\drawdisc}[1]{%
  \uncover#2{
    \point{start-disc}{#1}
    \node[style=node] (h) at (start-disc) {};
    \node[right=0.1cm of h] {$h_1$};

@@

\newcommand{\initialoverview}[1]{
  \point{start-initoverview}{#1};
  \node (obs-mom) at (start-initoverview) {$M \eqdef \Pr(\bx)$};
  \node (params) at ($(obs-mom) + (2cm, -2cm) + (-2cm, -2cm) + (0, -2cm)$) {$\theta$};

  \node[right=0.1cm of obs-mom] {Observed moments};
  \node[right=0.1cm of params] {Parameters};

  \draw[-latex] (obs-mom) -- (params);
}

\newcommand{\overview}[1]{
  \point{start-overview}{#1};
  \node (obs-mom) at (start-overview) {$M \eqdef \Pr(\bx)$};
  \node (cond-mom) at ($(obs-mom) + (2cm, -2cm)$) {$\mOpp{1}{1} \eqdef \Pr(\bx | \bh)$};
  \node (hid-marg) at ($(cond-mom) + (-2cm, -2cm)$) {$Z \eqdef \Pr(\bh)$};
  \node (params) at ($(hid-marg) + (0, -2cm)$) {$\theta$};

  \node[right=0.1cm of obs-mom] {Observed moments};
  \node[right=0.1cm of cond-mom] {Conditional moments};
  \node[right=0.1cm of hid-marg] {Hidden marginals};
  \node[right=0.1cm of params] {Parameters};

  \draw[-latex] (obs-mom) -- node[right] (obs-edge) {} (cond-mom);
  \draw[-latex] (cond-mom) -- node[right] (cond-edge) {} (hid-marg);
  \draw[-latex] (obs-mom) -- node[right] (hid-edge) {} (hid-marg);
  \draw[-latex] (hid-marg) -- node[right] (params-edge) {}    (params);
}
